%-------------------------
% Resume in Latex
% Author : Pranay Aryal
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Pranay Aryal} & 
  \textbf{drpranayaryal@gmail.com}\\
  \ & 502-416-8034 \\
  \ & \href{https://www.github.com/pranayaryal}{https://github.com/pranayaryal} \\
   \ & \href{https://www.pranaysite.com}{https://pranaysite.com} \\
\end{tabular*}





    

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
     \resumeSubheading
      {Humana}{Louisville, KY}
      {Software Engineer}{4/2018 - Present}
      \resumeItemListStart
  
        \item{\textbf{API - } Created an API service that is used by multiple internal teams (.Net Core, SQL Server)}
        \item{\textbf{CI/CD - }Deploy applications to a cloud-based service, \textbf{Pivotal Cloud Foundry},  using a CI/CD pipeline in \textbf{Azure Devops}}
        \item{\textbf{Feature Enhancements - } Add features to existing SOAP services based on business requirements, fix bugs in existing backend services on a large database (C\#, .NET, SQL and Pivotal Cloud Foundry, Git)}
         \item{\textbf{ETL - } Create ETL pipelines using SSIS packages. (SQL)}
          \item{\textbf{Security - } Fix security vulnerabilities highlighted by Checkmarx before pushing application to production. (.NET, C\#)}
          
          
      \resumeItemListEnd
      
    \resumeSubheading
      {Doe Anderson}{Louisville, KY}
      {Software Developer}{2/2018 - 4/2018}
      \resumeItemListStart
        \item
          { \textbf{Launched} email campaigns by integrating mailchimp, analyzed historical client data for insights, added new features to existing websites.
          (\textbf{Laravel/PHP}, \textbf{Vue.js} and Mailchimp, AWS-RDS, PySpark, Wordpress)}
      \resumeItemListEnd

    \resumeSubheading
      {Blackstone Media}{Louisville, KY}
      {Software Developer}{5/2015 - 7/2017}
      \resumeItemListStart
        \item
          {\textbf{Created value} for the client by launching an online payment system by which website visitors could make credit-card donations, created online dashboards, scraped websites to gather pricing data (\textbf{Laravel/PHP}, Angular.js,  MySql, Stripe API)}
         
    \resumeItemListEnd


      
      \resumeSubheading
      {Christian Medical College and Baptist Christian Hospital}{India}
      { Resident Physician }{2005 - 2011}
      \resumeItemListStart
       \item
          {Medical management of inpatients and outpatients}
          
      \resumeItemListEnd
     

  \resumeSubHeadingListEnd
  
\section{Relevant Projects}
    \resumeSubHeadingListStart
        \resumeItem
        {\href{https://github.com/pranayaryal/larcommerce}{Personal payments Website}}
        {Payment website using \textbf{Laravel 7.x}, \textbf{Stripe} and \textbf{React}. \href{}{https://github.com/pranayaryal/larcommerce}}
    
         \resumeItem
        {\href{https://github.com/pranayaryal/covid-sanity}{Covid Papers Website}}
        {Papers related to covid-19 using React. \href{}{https://github.com/pranayaryal/covid-sanity}}
       
         \resumeItem
        {\href{https://github.com/pranayaryal/ecommerce}{Ecommerce with React}}
        {Created a shopping cart using React Hooks and React's Context API. \href{https://github.com/pranayaryal/ecommerce}{https://github.com/pranayaryal/ecommerce}}
        
        \resumeItem
        {\href{https://github.com/pranayaryal/blog-bulma}{Blog site}}
        {Uses Gatsby.js. \href{https://github.com/pranayaryal/portfolio-site}{https://github.com/pranayaryal/portfolio-site}}
        
        \resumeItem
        {\href{https://github.com/pranayaryal/chords}{Ukulele Chords}}
        {Ukulele chords using React.js, \href{https://github.com/pranayaryal/chords}{https://github.com/pranayaryal/chords}}
        
         \resumeItem
        {\href{http://pranayaryal.github.io/planar}{Neural Networks and Logistic Regression in the browser}}
        {Use Tensorflow.js, \textbf{Vue.js}, HTML/CSS to compare a 4 layered neural network with logistic regression.  \href{https://pranayaryal.github.io/planar/}{https://pranayaryal.github.io/planar/}}
        

        
    \resumeSubHeadingListEnd
  
\section{Education}

    \resumeSubheading
      {Christian Medical College}{Ludhiana, India}
      {Medicine}{Jun. 1999 -- Dec. 2004}
      
\end{document}
